Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-04-15 Scripts/Initial_Analysis.Rmd
Working emerging function

```{r Ch3_setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

#### Library ####
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo",
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot" # for Juanito's map
)

@@

### Fun `GetSppDist`

@@

```{r GetSppDist, eval = F, echo = T}

@@

## Changes in Proportion

### Fun `EstPropChange`

@@

### Fun `EstTransIndex`

```{r funEstTransIndex, eval= F ,echo = T,warning = F,message = F}

# Function to determine whether or not a species is transboundary

# Varibales needed
# Spp: Species to be analized, data with presence/absence per gridcell
# Index_EEZ: Reference list of all INDEX that fall within EEZs
# EEZ_Size: Number of grid-cells that each EEZ has
# Neighbours: Reference list of neighbouring countries

# Needs getSppDist

#### For testing 
# Spp <- 600004  # Anchovie Equator, Chile and Peru
# Spp <- 600107 # Tuna Many RFMOs
# Spp <- 600004 # Argument 1 must have names (RFMO)
# Spp <- 600464 # Discrete species 
# Spp <- 600051 # One of Pierrs massive (wrong) discrete spp
# x <- c(600464, # Discreat spp in one nation
# 600059, # nowhere to be found spp
# 601352, # Discrete spp in two nations
# 600004) # transboundary spp
# Model <- "All"
# Coord <- CoorG
# 
# # For EEZ
# Neighbours <- Neighbours_Data
# Index_Code <- Index_Code

# __________________________________ #

# The function
EstTransIndex <- function(Spp,iyr,fyr,data_type,ensamble_list,Path,Neighbours){

  # Get model data from spps
  SppDist <- dbem_import(
    taxon_key = Spp,
    iyr <- iyr,
    fyr <- fyr,
    data_type <- "Abd",
    ensamble_list = ensamble_list,
    Path <- paste(data_path,"DBEM/",sep="")
  )

  #____________ Selecting only the transboundary nature of the species _________ #
  Trans_Spp <- SppDist %>%
    left_join(Neighbours,
              by= "index") %>% 
    filter(!is.na(value)) %>% 
    semi_join(Transboundary_spp, # filter only transboundary cases
              by = c("taxon_key","eez_name","eez_neighbour")
    )

  #Step 1.  Get EEZ id and Neighbour
  Neighbours_List <- Neighbours %>% 
    group_by(eez_name,eez_neighbour) %>% 
    summarise(n=n()) %>% 
    ungroup() %>% 
    select(-n)

  # Step 2. Determines the amount of grids present in each country
  Spp_Grid <- Trans_Spp %>% 
    group_by(taxon_key,
             eez_name,
             year,
             ensamble) %>% 
    summarise(n_spp_eez = length(unique(index))) %>% 
    left_join(Neighbours_List,
              by = "eez_name") %>% 
    filter(eez_name %in% Trans_Spp$eez_name, #Filter out unwanted Neighbours (those who don't have grids within but get included because they are Neighbours)
           eez_neighbour %in% Trans_Spp$eez_name)

      # Split dataframes to merge latter
    Territory_T <- Spp_Grid %>% 
      ungroup() %>% 
      select(
        taxon_key,
        Name=eez_name,
        n_spp_eez,
        year,
        ensamble
      )

    Neighbour_T <- Spp_Grid %>% 
      ungroup() %>% 
      select(
        taxon_key,
        n_spp_eez,
        Name=eez_neighbour,
        eez_name,
        year,
        ensamble
      )

    # Merge dataframes to get totals per Neighbourds
    area_index_d <- full_join(Territory_T,
                              Neighbour_T, 
                              by = c("Name","taxon_key","year","ensamble")
    ) %>%
      rowwise() %>%
      mutate(Spp_Total = sum(n_spp_eez.x,n_spp_eez.y,na.rm=T)) %>% # Total gridcelles per Neighbours
      distinct() %>% # Removes false duplicates from `full_join()`
      rename(eez_name = Name,
             eez_neighbour =eez_name,
             n_spp_Country = n_spp_eez.x,
             n_spp_Neighbour = n_spp_eez.y) %>% 
      mutate(area_index = n_spp_Country/Spp_Total) %>% 
      select(taxon_key,year,ensamble,eez_name,eez_neighbour,area_index) %>% 
      mutate(
        time_step = ifelse(year < 2000,"historical",
                           ifelse(year >= 2045 & year <= 2064, "mid",
                                  ifelse(year >= 2080, "n_end","NA")
                           )
        )
      ) %>%
      # Ensamble mean and sd
      ungroup() %>% 
      group_by(taxon_key,year,eez_name,eez_neighbour,time_step) %>% 
      summarise_at(vars("area_index"),
                   c(ensamble_mean=mean,
                     ensamble_sd=sd)
                   ) %>% 
      group_by(taxon_key,eez_name,eez_neighbour,time_step) %>% #Running mean
      mutate(RMean = rollmean(x = ensamble_mean,
                            5,
                            align = "right",
                            fill = ensamble_mean)
    )

    # Determine if changes
    natural_variation_d <- area_index_d %>% 
      ungroup() %>% #remove rowise
      filter(time_step == "historical") %>% 
      # Temporal mean
      group_by(taxon_key,eez_name,eez_neighbour) %>% 
      summarise_at(vars("ensamble_mean"),
                   c(hist_mean_index=mean,
                     hist_sd_index=sd)
      )

    ### Variation treshold
    variation_d <- area_index_d %>% 
      ungroup() %>% #remove rowise
      # Temporal mean
      group_by(taxon_key,time_step,eez_name,eez_neighbour) %>% 
      summarise_at(vars("RMean"),
                   c(mean_index=mean,
                     sd_index=sd)
      ) %>% 
      gather("variable","value",mean_index,sd_index) %>% 
      spread(time_step,value) %>% 
      mutate(larger_variation = ifelse(future > historical,"yes","no"))

    # William's index methodology
    trans_index_data <- area_index_d %>% 
      left_join(natural_variation_d,
                by = c("taxon_key","eez_name","eez_neighbour")) %>% 
      mutate(d_sd = ensamble_mean/sd_index) %>% 
      gather("variable","value",ensamble_mean:d_sd) %>% 
      ungroup() %>% 
      select(-time_step,-eez_neighbour) %>% 
      rowid_to_column() %>% 
      # spread(time_step,value) %>% 
      spread(eez_name,value) %>% 
      group_by(taxon_key,year,variable) %>% 
      summarise_at(vars("Chile","Ecuador","Peru"),
                   mean,na.rm=T)

    ggplot(area_index_d) +
      geom_ribbon(data=area_index_d,
                  aes(
                    x = as.numeric(year),
                    ymin=RMean-ensamble_sd,
                    ymax=RMean+ensamble_sd
                  ),
                  fill = "red",
                  alpha = 0.5
                  )+
      geom_line(
        aes(
          x = as.numeric(year),
          y = RMean
        )
      )  +
      facet_wrap(~eez_name + eez_neighbour,
                 scales = "free")

} # closes function

# __________________________________
# Test function
# __________________________________

### Fun `EstRangeIndex`

```{r load_data_per_ensamble, eval = F, echo = T}

#### Data needed (send to Control pannel latter)

# All ensambles
ensamble_list <- c(102,103)

# for dbem_impo_ensamble So we don't miss INDEX in different ensambles
world_grid <- tibble(index = seq(1,259200,1))
taxon_key <- 600005 #601477

EstRangeIndex <- function(taxon_key,iyr,fyr,ensamble_list){

  spp_data <- dbem_import(
    taxon_key = taxon_key,
    iyr <- 1951,
    fyr <- 2100,
    data_type <- "Abd",
    ensamble_list = ensamble_list,
    Path <- paste(data_path,"DBEM/",sep="")
  ) %>% 
    # Remove places where species is not destributed and set to cero differences between ensambles
    filter(!is.na(value)) %>% 
    spread(ensamble,value) %>% 
    gather(ensamble,value, -1:-3) %>% 
    mutate(value = ifelse(is.na(value),0,value)) %>% 
  # Include eez information
    left_join(index_code,
              by = "index") %>% 
    filter(!is.na(eezid))

  # Estimate mean eez centroid
  # centroid_data_eez <-  spp_data %>% 
  #   ungroup() %>% 
  #   group_by(taxon_key,ensamble,year,eezid,eez_name) %>% 
  #   top_n(1,value) %>% 
  #   group_by(year,taxon_key,ensamble,eezid,eez_name) %>% 
  #   summarise_at(vars(lon,lat),mean) %>%  # solves for multiple top 1
  #   rename(eez_centroid_lon = lon,
  #          eez_centroid_lat = lat) %>% 
  #   filter(!is.na(eezid))

  centroid_data_eez <-  spp_data %>% 
    ungroup() %>% 
    group_by(taxon_key,eezid,eez_name) %>%
    summarise_at(vars(lon,lat),mean) %>%  # solves for multiple top 1
    rename(eez_centroid_lon = lon,
           eez_centroid_lat = lat)

  # Visualization of  eez centroids
  # ggplot(spp_data) +
  #   geom_tile(
  #     aes(
  #     x = lon,
  #     y = lat,
  #     fill= eez_name
  #     )
  #   ) +
  #   geom_point(data = centroid_data_eez,
  #              aes(
  #                x = eez_centroid_lon,
  #                y = eez_centroid_lat,
  #                size = 1
  #              )
  #   )

# Estimate species distribution centroid
  centroid_spp <-  spp_data %>% 
    ungroup() %>% 
    group_by(taxon_key,ensamble,year) %>% 
    top_n(1,value) %>% 
    group_by(taxon_key,ensamble,year) %>% 
    summarise_at(vars(lon,lat),mean) %>%  # solves for multiple top 1
    rename(spp_centroid_lon = lon,
           spp_centroid_lat = lat)

  ggplot(centroid_spp) +
    geom_point(
      aes(
        x = spp_centroid_lon,
        y = spp_centroid_lat,
        size = as.numeric(year)#,
        # shape = eez_name
      )
    ) +
    geom_point(data = centroid_data_eez,
               aes(
                 x = eez_centroid_lon,
                 y = eez_centroid_lat,
                 color = eez_name
               )
    ) +
    facet_wrap(~ensamble)

# Estimate Transboundary Index
  trans_index_data <- centroid_data_eez %>% 
    left_join(centroid_spp,
              by = c("taxon_key") # removed year
              ) %>% 
    ungroup() %>% 
    # select(year,eez_name,ensamble,spp_centroid_lon,spp_centroid_lat,eez_centroid_lon, eez_centroid_lat) %>%
    rowwise() %>%
    mutate(d_eez = distm(c(eez_centroid_lon, eez_centroid_lat),c(spp_centroid_lon, spp_centroid_lat), fun = distHaversine))

trans_index_sd_data <- trans_index_data %>% 
  ungroup() %>% 
  filter(year <2000) %>% 
  group_by(eez_name,ensamble) %>% 
  summarise(
    s_sd = sd(d_eez)
  )

final_trans_index_data <- trans_index_data %>% 
  left_join(trans_index_sd_data,
            by = c("eez_name","ensamble")
            ) %>% 
  mutate(da_dsd = d_eez/s_sd) %>% 
  filter(eez_name != "Colombia (Pacific)") %>% 
  select(year,eez_name,ensamble,da_dsd) %>% 
  spread(eez_name,da_dsd) %>% 
  mutate(Trans_Index = `Mexico (Atlantic)`-`USA (Gulf of Mexico)`/2) %>% 
  ungroup() %>% 
  group_by(ensamble) %>% # Running mean as Kleisner & Pauly 2012
  mutate(RMean = rollmean(x = Trans_Index,
                            5,
                            align = "right",
                            fill = Trans_Index)
    )

ggplot(final_trans_index_data) +
  geom_line(
    aes(
      x = as.numeric(year),
      y = RMean,
      color = ensamble
    )
  ) +
  geom_line(data = final_trans_index_data,
    aes(
      x = as.numeric(year),
      y = Trans_Index,
      color = ensamble
    ),
    linetype = "dashed",
    alpha = 0.5
  ) +
  facet_wrap(~ensamble,
             ncol= 1)

  # %>% 
  #   filter(ensamble == 102) %>% 
  #   select(year,ensamble,eez_name,d_eez) %>% 
  #   spread(eez_name,d_eez) %>% 
  #   mutate()

  Year_MCP <-  spp_data %>% 
    # Aggregate MCP per EEZ
    group_by(taxon_key,eezid,eez_name,ensamble,year) %>% 
    summarise(eez_mcp = sum(value,na.rm=T)) %>% 
    # Ensamble mean
    group_by(taxon_key,eezid,eez_name,year) %>% 
    summarise(ensamble_mean = mean(eez_mcp,na.rm=T),
              ensamble_sd = sd(eez_mcp,na.rm=T)
              )

  # Test 
  # ggplot(spp_data) +
  #   geom_line(
  #     aes(
  #       x = as.numeric(year),
  #       y = ensamble_mean
  #     )
  #   ) +
  #   geom_point(
  #     aes(
  #       x = as.numeric(year),
  #       y = ensamble_mean+ensamble_sd
  #     )
  #   ) +
  #   geom_point(
  #     aes(
  #       x = as.numeric(year),
  #       y = ensamble_mean-ensamble_sd
  #     )
  #   ) +
  #   facet_wrap(~eez_name)

  } # close function

## Control Panel

```{r control_panel, eval = F}

year_df <- tibble(year =  c(seq(1995,2014,1), seq(2041,2060,1), seq(2080,2099,1)),
                  time_period = c(rep("Today", 20), rep("Mid Century", 20), rep("End of Century", 20))
                  )

data_type <- "Catch"
ensamble_list <- seq(102,111,1)
world_grid <- tibble(index = seq(1,259200,1))

spp_list <- unique(Transboundary_spp$taxon_key)

## Proportion Routine

@@

@@

@@

# Get the center poligon of each EEZ for map source/target
coords <- as.data.frame(st_centroid(World_eez_sf)) %>% 
  ungroup() %>% 
  select(eez_name,geometry) %>% 
  separate(col = geometry, into = c("longitude", "latitude"), sep = "\\,") %>% 
  # Manually fix issues
  mutate(
    longitude = ifelse(
      eez_name == "Fiji", 178.065033,
      ifelse(eez_name == "Tuvalu",177.6493,
             ifelse( eez_name == "New Zealand",174.8860,
                     ifelse( eez_name == "USA (Alaska, Subarctic)",-145.8860,
                             ifelse( eez_name == "Brazil",-36.937,longitude
                             )
                     )
             )
      )
    )
  )

>>>>

```{r setup, eval = T, echo=F, warning=F,message=F, results='hide'}

@@

#### Library ####
packages <- c(
  "tidyverse",
  "here", # for dbem_import `here()`
  "data.table", #dbem_import `fread()`
  "readxl", # for reading excell files
  "janitor", # for clearing names
  "geosphere", # estimate distances between points `distm()`
  "ggrepel",
  "zoo",
  "parallel", # for mclapply,
  "sf", # for mapping
  "st", # for mapping
  "rgdal", #Spatial analysis
  "tools", #Spatial analysis 
  "zeallot", # for Juanito's map
  "gmt" # for estimating distances between points
)

@@

### Fun `dbem_import`

@@

```{r dbem_import, eval = F, echo = T}

@@

## Determine Coords centroids and Neighbouring ids

```{r, get_eez_centroids, eval = F}

# Get the center poligon of each EEZ for map source/target with st_centroid
coords <- as.data.frame(st_centroid(World_eez_sf)) %>% 
  ungroup() %>% 
  select(eez_name,geometry) %>% 
  separate(col = geometry, into = c("longitude", "latitude"), sep = "\\,") %>% 
  # Manually fix issues
  mutate(
    longitude = ifelse(
      eez_name == "Fiji", 178.065033,
      ifelse(eez_name == "Tuvalu",177.6493,
             ifelse( eez_name == "New Zealand",174.8860,
                     ifelse( eez_name == "USA (Alaska, Subarctic)",-145.8860,
                             ifelse( eez_name == "Brazil",-36.937,longitude
                             )
                     )
             )
      )
    )
  )

write_csv(coords,
          "eez_centroids.csv")

# Get id of neighbouring pairs
Neighbours_spp <- Transboundary_spp %>% 
  group_by(eez_name,eez_neighbour) %>% 
  summarise(n=n()) %>% 
  ungroup() %>% 
  select(-n) %>% 
  rownames_to_column("neighbour_id")

#  set ids 
df1 <- Neighbours_spp
df2 <- Neighbours_spp
colnames(df2) <- c("neighbour_id", "eez_neighbour", "eez_name")

df_full <- bind_rows(df1, df2) %>% 
  group_by(eez_neighbour,eez_name) %>% 
  summarise(neighbour_id = min(neighbour_id))

# write_csv(df_full, "Neighbours_eez_id.csv")

## Estimating Proportion Change

#### Fun `EstPropChange`

@@

#### Proportion routine

@@

## Estimating emerging year

#### Fun `TransIndex`

```{r TransIndex, eval = F, echo = T}

TransIndex <- function(Spp,year, data_type = "Catch",ensamble_list,path,Neighbours,eez_centroid){

  # ----------------- #
  # Get Species Centrodis
  #  ---------------- #

  # Get model data from spps
  Spp_Dist <- bind_rows(
    lapply(
      ensamble_list,
      dbem_import,
      taxon_key = Spp,
      year = year,
      data_type = data_type,
      path = path
    )
  )

  print(Spp)

  #____________ Selecting only the transboundary nature of the species _________ #
  Trans_Spp <- Spp_Dist %>%
    left_join(index_code,
              by= "index") %>% 
    filter(!is.na(value)) %>% 
    semi_join(Transboundary_spp, # filter only transboundary cases
              by = c("taxon_key","eez_name")
    )

  # Step
  nr <- nrow(Trans_Spp)
  if(nr > 0){

    # Filter eez by those transboundary
  unique_eez <- unique(Trans_Spp$eez_name)

  Neighbours_combo <- Neighbours %>% 
    filter(eez_name %in% unique_eez,
           eez_neighbour %in% unique_eez)

    # Get the centroid of each country
    EEZ_centroid <- eez_centroid %>% 
      filter(eez_name %in% Trans_Spp$eez_name) %>% 
      mutate(taxon_key = Spp)

    Ids <- unique(Neighbours_combo$neighbour_id)

    for(i in 1:length(Ids)){

      EEZ_ids <- Neighbours_combo %>% 
        filter(neighbour_id == Ids[i])

      Sub_Trans_Spp <- Trans_Spp %>% 
        filter(eez_name %in% EEZ_ids$eez_name)

      Sub_EEZ_centroid <- EEZ_centroid %>% 
        filter(eez_name %in% EEZ_ids$eez_name)

      # Centroid is defined as the tile with the higest species value
      Centroids <- Sub_Trans_Spp %>% 
        left_join(EEZ_ids, by = "eez_name") %>% 
        group_by(taxon_key,year,ensamble,neighbour_id) %>%  # for whole distribution
        top_n(1,value) %>% 
        distinct(value,year, .keep_all = TRUE) %>%  # removes duplicates when tile is in between EEZs
        left_join(Sub_EEZ_centroid, by = "taxon_key") %>%
        select(eez_name =eez_name.y, everything() ,-eez_name.x)

      # Estimate distances between spp centroid and EEZ centroid
      Distance_Data <- Centroids %>%
        rename(
          catch_lon = lon,
          catch_lat = lat,
          eez_lon = longitude,
          eez_lat= latitude
        ) %>% 
        # Estimate the distance between centriods
        mutate(
          distance = geodist(eez_lon, eez_lat, catch_lon, catch_lat, units="km")
        ) %>% 
        select(taxon_key,eez_name,neighbour_id,ensamble,year,distance)

      # Historical mean and sd of distance
      historical <- Distance_Data %>%
        filter(year <= 2000) %>%
        ungroup() %>%
        group_by(taxon_key,ensamble,eez_name,neighbour_id) %>%
        summarise_at(vars("distance"),
                     c(hd_temp_mean=mean,
                       hd_temp_sd=sd)
        )

      # Future results
      future <- Distance_Data %>% 
        filter(year > 2000)

      # Transboundary Index
      Trans_index <- Distance_Data %>% 
        left_join(historical,
                  by = c("taxon_key","eez_name","ensamble","neighbour_id")
        ) %>%
        # Re arrenging table for mutate
        gather("variable","value",distance:hd_temp_sd) %>%
        ungroup()

      Partial <- Trans_index %>% 
        mutate(
          names = ifelse(eez_name ==Sub_EEZ_centroid$eez_name[1],paste("Country_A",variable,sep="_"),paste("Country_B",variable,sep="_"))
        ) %>%
        select(-eez_name,-variable) %>%
        spread(names,value) %>% 
        # mutate index
        mutate(
          trans_index = (Country_A_distance/Country_A_hd_temp_sd - Country_B_distance/Country_B_hd_temp_sd)^2
        ) %>% 
        group_by(taxon_key,ensamble,neighbour_id) %>% 
        mutate(RMean = rollmean(x = trans_index, 
                                10, 
                                align = "right", 
                                fill = trans_index)
        ) %>% 
        filter(year > 1960) %>% 
        select(taxon_key,neighbour_id,year,ensamble,trans_index,RMean)

      # Average of 10 years mean of ensamble members results
      mean_sd_index <- Partial %>% 
        group_by(taxon_key,year,neighbour_id) %>% 
        summarise_at(vars("RMean"),
                     c(trend=mean,
                       ensamble_sd=sd)
        )

      # Estimate noice from ensamble members
      historic_sd <- mean_sd_index %>% 
        filter(year < 2000) %>% 
        group_by(taxon_key) %>% 
        summarise_at(vars("trend"),
                     c(hist_mean=mean,
                       noise=sd)
        )

      # Plot the result, bruh
      # ggplot() +
      #   geom_line(data = mean_sd_index,
      #             aes(
      #               x = year,
      #               y = trend
      #             )
      #   ) +
      #   geom_ribbon(data = mean_sd_index,
      #               aes(x=year,
      #                   ymin=historic_sd$hist_mean-historic_sd$noise,
      #                   ymax=historic_sd$hist_mean+historic_sd$noise),
      #               alpha = 0.5,
      #               fill = "grey50"
      #   ) +
      #   geom_line(data = mean_sd_index,
      #             aes(
      #               x = year,
      #               y = historic_sd$hist_mean
      #             ),
      #             colour = "grey50"
      #   ) +
      #   geom_point(data = subset(mean_sd_index, trend > (historic_sd$hist_mean+historic_sd$noise) | trend < (historic_sd$hist_mean-historic_sd$noise)),
      #              aes(
      #                x = year,
      #                y = trend,
      #                colour = "red",
      #              ),
      #              shape = 1,
      #              size = 3
      #   ) +
      #   geom_vline(xintercept = 2000,colour="blue",alpha = 0.5) +
      #   theme_classic()

      # #     
      Final_Result <- mean_sd_index %>%
        filter(year > 2000,
               trend > (historic_sd$hist_mean+historic_sd$noise) |
                 trend < (historic_sd$hist_mean-historic_sd$noise)
        ) %>%
        group_by(taxon_key,neighbour_id) %>%
        summarise(emerging_yr= min(year)) %>%
        left_join(EEZ_ids) %>%
        ungroup() %>%
        select(taxon_key,eez_name,eez_neighbour,emerging_yr)

      if(i == 1){
        f_df <- Final_Result
      }else{
        f_df <- bind_rows(f_df,Final_Result)
      }
    }

    return(f_df)

    print("no share data")

    f_df <- tibble(
      taxon_key = Spp,
      eez_name = NA,
      emerging_yr = NA
    )

  return(f_df)

#  #One spp works 
# suppressMessages(
# x <-  TransIndex(Spp = 600245,
#              year,
#              data_type = "Catch",
#              ensamble_list,
#              path,
#              Neighbours = Neighbours,
#              eez_centroid)
# )
# Multiple spp

# spp_list <- c(600004,
#               600005,
#               600245,
#               600006
#               )
# 
# suppressMessages(
#   suppressWarnings(
#     Test <- bind_rows(
#       lapply(spp_list,
#              TransIndex,
#              year,
#              data_type = "Catch",
#              ensamble_list,
#              path,
#              Neighbours,
#              eez_centroid
#       )
#     )
#   )
# )

#### Emerging Control Panel

```{r Emerging_control_panel, eval = F}

year_df <- tibble(year =  c(seq(1951,2000,1), seq(2001,2099,1)),
                  time_period = c(rep("historic", 50), rep("future", 99))
                  )

data_type <- "catch"
ensamble_list <- seq(102,103,1)
world_grid <- tibble(index = seq(1,259200,1))
path = DBEM_path

eez_centroid <- read.csv("~/GitHub/TransEmergence/Temporal_Data/Spatial/eez_centroids.csv", header=TRUE)

Neighbours <- read.csv(paste(data_path,"Spatial/Neighbours_eez_id.csv",sep="")) %>% clean_names()

#### Emerging Routine
```{r Emerging_routine, eval = F, echo = F}

####_______________________ ####
# Estimating year of eergence
####_______________________ ####

spp_list <- c(600004,
              600005,
              600245,
              600006
              )

suppressMessages(
  suppressWarnings(
    Test <- bind_rows(
      lapply(spp_list,
             TransIndex,
             year,
             data_type = "Catch",
             ensamble_list,
             path,
             Neighbours,
             eez_centroid
      )
    )
  )
)

@@

coords <- read.csv(coords)

@@
